Multi sky-view\\ 3D aerosol distribution recovery

### 2013-09-23 article.tex

\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}. In
Figs.~\ref{fig:results}(a) and (b), the single-scattering model was used both
in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}. The total estimation
error can be quantified by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
The overall mass is recovered, but for 6.5\% loss. For local errors,
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
$\epsilon=0.65$.

>>>>

\Cref{fig:results} shows estimation results, corresponding to the
original distributions of \cref{fig:distributions}. 
\hl{
In these simulations the atmosphere domain was defined over a
$20\times20 \times 40$ grid. Thirty six cameras were placed
$\sim7$km apart on a $6\times6$ grid.
}
In Figs.~\ref{fig:results}(a) and (b), the single-scattering model was
used both
in rendering of the raw images, and in the estimation algorithm. In
Figs.~\ref{fig:results}(c) and (d), the MC model (multiple scattering)
rendered the raw images, over which the estimation algorithm
ran. Overall, the distributions, the density order of magnitude and
values are consistent.
Errors in Figs.~\ref{fig:results}(a) and (b) stem from random noise, which had
been induced in the raw images. Errors are larger when MC is used to
render the images, since high-order scattering is not accounted for in
the algorithm of \cref{sec:inverse-problem}. The total estimation
error can be quantified by the aerosol mass that is over and under-estimated
in all voxels, relative to the total aerosol mass in the scene. Using the $\ell_1$ norm, 
the total mass relative difference is
$(\|\hat{\bm n}\|_1 - \|{\bm n}^{\rm true} \|_1) / \| {\bm n}^{\rm true} \|_1$.
The overall mass is recovered, but for 6.5\% loss. For local errors,
 $\epsilon=\|
\hat{\bm n} - {\bm n}^{\rm true} \|_1 / \| {\bm n}^{\rm true} \|_1$.
  In Figs.~\ref{fig:results}(a) and (b), respectively $\epsilon=0.14$ and
$\epsilon=0.20$.  In Figs.~\ref{fig:results}(c) and (d), both cases have
$\epsilon=0.65$.
